Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-01-30 ms.tex
Fixing typo plus a particular table entry

\begin{table*}
\centering
\begin{minipage}{18cm}
\caption{Summary of Numerical Solutions}
\begin{tabular}{lccccccccccccc}
\hline
{$M_{\bullet,8}$} & {$v_{w}$} & {$\Gamma^{(a)}$} & {$r_b$} & {$\dot{M}/\dot{M}_{\rm edd}$} & {$(t_{\rm cool}/t_{\rm ff})_{r_s}$} & {comments}\\
\hline
0.01 & 300 & 0.8 & N/A & $ 3.2 \times 10^{ -4 }$ & 4.7 & rb in fact
unresolved \\
0.01 & 600 & 0.8 & N/A & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
10^{ 2 }$ &  rb in fact unresolved\\
0.01 & 1200 & 0.8 & N/A & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
10^{ 4 }$ &  rb in fact unresolved\\
0.1 & 300 & 0.8 & 100.0 & $ 2.5 \times 10^{ -3 }$ & 0.29 & energy
cons on outer grid \\
0.1 & 600 & 0.8 & 100.0 & $ 1.8 \times 10^{ -4 }$ & 97 &  \\
0.1 & 1200 & 0.8 & 100.0 & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
10^{ 3 }$ &  \\
1 & 300 & 0.8 & 100.0 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{
  -2 }$ &  TI\\
1 & 600 & 0.8 & 100.0 & $ 7.3 \times 10^{ -4 }$ & 21 &  \\
1 & 1200 & 0.8 & 100.0 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{
  3 }$ &  \\
1 & 300 & 0.8 & 50.0 & $ 8.2 \times 10^{ -3 }$ & 0.19 &  \\
1 & 300 & 0.8 & 200.0 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{
  -2 }$ &  TI/convergence \\
%1 & 300.0 & 0.8 & 300.0 & $ 5.2 \times 10^{ -2 }$ & $ 9.8 \times 10^{
%  -3 }$ &  TI/convergence\\
1 & 300 & 0.8 & 400.0 &  &  &  TI/run unsuccessful\\
0.1 & 300 & 0.8 & 50.0 & $ 2.0 \times 10^{ -3 }$ & 0.46 &  \\
0.1 & 300 & 0.8 & 200.0 & $ 5.3 \times 10^{ -3 }$ & 0.12 &  TI/convergence\\
%0.1 & 300.0 & 0.8 & 300.0 & $ 7.2 \times 10^{ -3 }$ & $ 6.7 \times
%10^{ -2 }$   & TI/convergence  \\
0.1 & 300 & 0.8 & 400.0 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times
10^{ -2 }$ & TI/convergence \\
0.01 & 1200 & 0.1 & N/A & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times
10^{ 4 }$ &  rb is unsresolved\\
0.1 & 1200 & 0.1 & N/A & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{
  3 }$ &  tried run in which rb=100 pc was resolved what would happen if rb=400 pc?\\
0.01 & 1200 & 0.1 & 100.0 & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times 10^{ 4 }$ &  \\
0.1 & 1200& 0.1 & 100.0 & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{ 3 }$ &  \\
1 & 1200 & 0.1 & 100.0 & $ 6.0 \times 10^{ -5 }$ & $ 8.6 \times 10^{ 2 }$ &  \\
1 & 1200 & 0.1 & 50.0 & $ 4.9 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 3 }$ &  \\
1 & 1200 & 0.1 & 200.0 & $ 1.0 \times 10^{ -4 }$ & $ 3.4 \times 10^{ 2 }$ &  \\
%1 & 1200.0 & 0.1 & 300.0 & $ 1.9 \times 10^{ -4 }$ & $ 1.3 \times 10^{ 2 }$ &  convergence\\
1 & 1200 & 0.1 & 400.0 & $ 1.8 \times 10^{ -2 }$ & 0.37 &  TI/convergence\\
\hline
\label{table:models}  
\end{tabular}
$^{(a)}$ Inner power-law index of stellar Nuker profile.  $^{(b)}$ Break radius of stellar Nuker profile.
\end{minipage}
\end{table*}

@@

For $\vw/\sigma \gg 1$ the value $\rs/\rinf$ does not depend on break
radius, $r_b$. On the other hand for $\vw/\sigma \simeq 1$, $\rb$ does
have an effect. Notice that near where the solid analytic curve
diverges there are three green square, one over the other. These
points correspond to models with the same $\Mbh (10^7 \Msun)$, $\vw
(300 {\rm km/s})$, and $\Gamma (0.8)$, but different values of the
break radius: from top to bottom 50 pc, 100 pc, and 400 pc.  
%% AG: Describe conservation checks to additionally validate the results.

>>>>

\begin{table*}
\centering
\begin{minipage}{18cm}
\caption{Summary of Numerical Solutions}
\begin{tabular}{lccccccccccccc}
\hline
{$M_{\bullet,8}$} & {$v_{w}$} & {$\Gamma^{(a)}$} & {$r_b$} & {$\dot{M}/\dot{M}_{\rm edd}$} & {$(t_{\rm cool}/t_{\rm ff})_{r_s}$} & {comments}\\
\hline
0.01 & 300 & 0.8 & N/A & $ 3.2 \times 10^{ -4 }$ & 4.7 & rb in fact
unresolved \\
0.01 & 600 & 0.8 & N/A & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
10^{ 2 }$ &  rb in fact unresolved\\
0.01 & 1200 & 0.8 & N/A & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
10^{ 4 }$ &  rb in fact unresolved\\
0.1 & 300 & 0.8 & 100.0 & $ 2.5 \times 10^{ -3 }$ & 0.29 & \\
0.1 & 600 & 0.8 & 100.0 & $ 1.8 \times 10^{ -4 }$ & 97 &  \\
0.1 & 1200 & 0.8 & 100.0 & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
10^{ 3 }$ &  \\
1 & 300 & 0.8 & 100.0 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{
  -2 }$ &  TI\\
1 & 600 & 0.8 & 100.0 & $ 7.3 \times 10^{ -4 }$ & 21 &  \\
1 & 1200 & 0.8 & 100.0 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{
  3 }$ &  \\
1 & 300 & 0.8 & 50.0 & $ 8.2 \times 10^{ -3 }$ & 0.19 &  \\
1 & 300 & 0.8 & 200.0 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{
  -2 }$ &  TI/convergence \\
%1 & 300.0 & 0.8 & 300.0 & $ 5.2 \times 10^{ -2 }$ & $ 9.8 \times 10^{
%  -3 }$ &  TI/convergence\\
1 & 300 & 0.8 & 400.0 &  &  &  TI/run unsuccessful\\
0.1 & 300 & 0.8 & 50.0 & $ 2.0 \times 10^{ -3 }$ & 0.46 &  \\
0.1 & 300 & 0.8 & 200.0 & $ 5.3 \times 10^{ -3 }$ & 0.12 &  TI/convergence\\
%0.1 & 300.0 & 0.8 & 300.0 & $ 7.2 \times 10^{ -3 }$ & $ 6.7 \times
%10^{ -2 }$   & TI/convergence  \\
0.1 & 300 & 0.8 & 400.0 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times
10^{ -2 }$ & TI/convergence \\
0.01 & 1200 & 0.1 & N/A & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times
10^{ 4 }$ &  rb is unsresolved\\
0.1 & 1200 & 0.1 & N/A & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{
  3 }$ &  tried run in which rb=100 pc was resolved what would happen if rb=400 pc?\\
0.01 & 1200 & 0.1 & 100.0 & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times 10^{ 4 }$ &  \\
0.1 & 1200& 0.1 & 100.0 & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{ 3 }$ &  \\
1 & 1200 & 0.1 & 100.0 & $ 6.0 \times 10^{ -5 }$ & $ 8.6 \times 10^{ 2 }$ &  \\
1 & 1200 & 0.1 & 50.0 & $ 4.9 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 3 }$ &  \\
1 & 1200 & 0.1 & 200.0 & $ 1.0 \times 10^{ -4 }$ & $ 3.4 \times 10^{ 2 }$ &  \\
%1 & 1200.0 & 0.1 & 300.0 & $ 1.9 \times 10^{ -4 }$ & $ 1.3 \times 10^{ 2 }$ &  convergence\\
1 & 1200 & 0.1 & 400.0 & $ 1.8 \times 10^{ -2 }$ & 0.37 &  TI/convergence\\
\hline
\label{table:models}  
\end{tabular}
$^{(a)}$ Inner power-law index of stellar Nuker profile.  $^{(b)}$ Break radius of stellar Nuker profile.
\end{minipage}
\end{table*}

@@

For $\vw/\sigma \gg 1$ the value $\rs/\rsoi$ does not depend on break
radius, $r_b$. On the other hand for $\vw/\sigma \simeq 1$, $\rb$ does
have an effect. Notice that near where the solid analytic curve
diverges there are three green square, one over the other. These
points correspond to models with the same $\Mbh (10^7 \Msun)$, $\vw
(300 {\rm km/s})$, and $\Gamma (0.8)$, but different values of the
break radius: from top to bottom 50 pc, 100 pc, and 400 pc.  
%% AG: Describe conservation checks to additionally validate the results.
